CRUSE to Safe Cycling in Ireland

### 2023-10-07 paper.qmd
naas and newbridge godutch

# # Uncomment the following line to produce the cover page
author:
  - name: Robin Lovelace
    email: r.lovelace@leeds.ac.uk
    corresponding: true
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Joey Talbot
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Eugeni Vidal-Tortosa
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Hussein Mahfouz
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Elaine Brick
    affiliations:
      - name: AECOM
        address: Unit 6, Galway Technology Park, Parkmore, Galway, Ireland
  - name: Peter Wright
    affiliations:
      - name: AECOM
        address: Winslade House, Winslade Park, Manor Drive, Clyst St Mary, EXETER, EX5 1FY, UK
  - name: "Gary O'Tool"
    affiliations:
      - name: AECOM
        address: Unit 6, Galway Technology Park, Parkmore, Galway, Ireland
  - name: Dan Brennan
    affiliations:
      - name: Transport Infrastructure Ireland
        address: Parkgate Business Centre, Parkgate Street, Dublin 8, D08 DK10, Ireland
  - name: Suzanne Meade
    affiliations:
      - name: Transport Infrastructure Ireland
        address: Parkgate Business Centre, Parkgate Street, Dublin 8, D08 DK10, Ireland
abstract: |
  Under the EU Road infrastructure safety management (RISM) directive, the National Road Safety Strategy (RSS) and the Climate Action Plan, Transport Infrastructure Ireland (TII) has a remit for road safety and decarbonizing a predominantly road-based network in Ireland.

@@

-   Calculation of hundreds-of-thousands of routes, which is beyond the terms of service of the free API.
-   Making changes to the routing profiles, including allowing routing on trunk roads, which are sometimes avoided in the default routing profiles.
-   Control over the version of OSM data being used for the routing, allowing regular updates to the route networks as OSM data is updated.

@@

::: {#fig-route-types layout-nrow="2"}
![](images/paste-5.png)

![](images/paste-6.png)

Illustration of the Fastest and Quietest route networks for central and East Limmerick.
:::

@@

::: {#fig-scenarios}
![](images/paste-7.png)

Distance-mode share graph for Limerick used to communicate the different scenarios.
Source: county level view for Limerick in the open access CRUSE Tool at <https://cruse.bike/limerick>.
:::

>>>>

# # Uncomment the following line to produce the cover page
author:
  - name: Robin Lovelace
    email: r.lovelace@leeds.ac.uk
    corresponding: true
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Joey Talbot
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Eugeni Vidal Tortosa
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Hussein Mahfouz
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Elaine Brick
    affiliations:
      - name: AECOM
        address: Unit 6, Galway Technology Park, Parkmore, Galway, Ireland
  - name: Peter Wright
    affiliations:
      - name: AECOM
        address: Winslade House, Winslade Park, Manor Drive, Clyst St Mary, EXETER, EX5 1FY, UK
  - name: "Gary O'Tool"
    affiliations:
      - name: AECOM
        address: Unit 6, Galway Technology Park, Parkmore, Galway, Ireland
  - name: Dan Brennan
    affiliations:
      - name: Transport Infrastructure Ireland
        address: Parkgate Business Centre, Parkgate Street, Dublin 8, D08 DK10, Ireland
  - name: Suzanne Meade
    affiliations:
      - name: Transport Infrastructure Ireland
        address: Parkgate Business Centre, Parkgate Street, Dublin 8, D08 DK10, Ireland
abstract: |
  Under the EU Road infrastructure safety management (RISM) directive, the National Road Safety Strategy (RSS), and the Climate Action Plan Transport Infrastructure Ireland (TII) has a remit for road safety and decarbonizing a predominantly road-based network in Ireland.

@@

-   Calculation of hundreds-of-thousands of routes, which is against the terms of service of the free API.
-   Making changes to the routing profiles, including allowing routing on trunk roads, which are not permitted in the default routing profiles.
-   Control over the version of OSM data being used for the routing, allowing regular updates to the route networks as OSM data is updated.

@@

<!-- ::: {#fig-route-types layout-nrow="2"} -->

<!-- ![](images/paste-5.png) -->

<!-- ![](images/paste-6.png) -->

<!-- Illustration of the Fastest and Quietest route networks for central and East Limmerick. -->

<!-- ::: -->

::: {#fig-route-types layout-nrow="2"}
![](images/naas_quietest_godutch.png){width="250"}

![](images/naas_fastest_godutch.png){width="250"}

![](images/newbridge_quietest_godutch.png){width="250"}

![](images/newbridge_fastest_godutch.png){width="250"}

Illustration of the Quietest (left) and Fastest (right) route networks for Naas (top) and Newbridge (bottom).
:::

@@

::: {#fig-scenarios}
<!-- ![](images/paste-7.png) -->

![](images/scenarios_kildare.png)

Distance-mode share graph for Kildare used to communicate the different scenarios.
Source: county level view for Kildare in the open access CRUSE Tool at <https://cruse.bike/kildare>.
:::
